\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muturi David} \\ \vspace{1pt} 
    \textbf{ Software Engineer } \\ \vspace{1pt}
    \href{mailto:muturidavid854@gmail.com}{\textcolor{blue}{muturidavid854@gmail.com}} $|$
    \href{https://linkedin.com/in/tushdev}{\textcolor{blue}{linkedin.com/in/tushdev}} $|$
    \href{https://github.com/tushcmd}{\textcolor{blue}{github.com/tushcmd}} $|$
    \href{https://tushdev.co/}{\textcolor{blue}{tushdev.co}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kenyatta University}{Nairobi, Kenya}
      {Nursing School (Dropped Out)}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Resident}{Sep. 2024 -- Present}
      {\textcolor{blue}{\href{https://headstarter.co/}{Headstarter Accelerator}}}{}
      \resumeItemListStart
        \resumeSubItem{Engaged in a 14-week accelerator, focusing on AI and software engineering projects like churn prediction, real-time voice AI, and LLM-based financial automation.}
        \resumeSubItem{Collaborated in teams to build and deploy AI-powered applications, incorporating tools such as Vercel, Hugging Face, and OpenAI.}
        \resumeSubItem{Actively involved in code reviews, technical discussions, and daily sprints following agile methodologies.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Fellow}{Jul. 2024 -- Sep. 2024}
      {\textcolor{blue}{\href{https://headstarter.co/}{Headstarter AI}}}{Track C}
      \resumeItemListStart
        \resumeSubItem{Developed and deployed multiple solo and team projects, including a personal website, pantry tracker, AI customer support system, and AI-powered flashcards with Stripe integration.}
        \resumeSubItem{Worked with technologies including HTML, CSS, ReactJS, NextJS, Firebase, OpenAI API, and AWS.}
        \resumeSubItem{Collaborated in teams to build scalable and efficient web applications, following agile methodologies with daily sprints and incorporated CI/CD practices for iterative deployment.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
          {\textcolor{blue}{\href{https://flash-cards-five-xi.vercel.app/}{Flashcards SaaS}}}{}{\emph{Next.js, Clerk, Firebase, OpenAI, Stripe}}{}
          \resumeItemListStart
            \resumeSubItem{Built a flashcard SaaS application with authentication, payment integration, and OpenAI-powered flashcard generation.}
            \resumeSubItem{Implemented CRUD features with Firebase Firestore and handled subscriptions using Stripe.}
          \resumeItemListEnd
          
      \resumeSubheading
          {\textcolor{blue}{\href{https://ai-customer-support-rho.vercel.app/}{AI Customer Support Chat Bot}}}{}{\emph{Next.js, Shadcn UI, Next-auth, Prisma, PostgreSQL, Neon, OpenAI, TailwindCSS}}{}
          \resumeItemListStart
            \resumeSubItem{Developed an AI-powered customer support chatbot with a responsive interface, authentication, and feedback features using Next.js and the OpenAI API.}
            \resumeSubItem{Implemented a PostgreSQL database with Prisma and deployed using Neon for scalable data storage and retrieval.}
          \resumeItemListEnd
          
      \resumeSubheading
          {\textcolor{blue}{\href{https://ram-rag.vercel.app/}{Rate a Mechanic RAG App}}}{}{\emph{Next.js, Shadcn UI, OpenAI, Pinecone, TailwindCSS}}{}
          \resumeItemListStart
            \resumeSubItem{Built a RAG AI assistant for rating mechanics using Next.js, with vector search capabilities provided by Pinecone and intelligent responses using OpenAI.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------HACKATHONS-----------
\section{Hackathons}
    \resumeSubHeadingListStart
      \resumeSubheading
          {\textcolor{blue}{\href{https://github.com/tushcmd/olo-scraper}{OloScraper}}}{}{\emph{React, Node.js, Express.js, MongoDB, Puppeteer, TailwindCSS}}{}
          \resumeItemListStart
            \resumeSubItem{Developed a full-stack web scraping application that simulates browser-like interactions using a headless browser. Users can input a URL, and the application scrapes data and performs specified actions.}
          \resumeItemListEnd
          
      \resumeSubheading
          {Rilla Voice}{}{\emph{React, TypeScript, Node.js, AWS Lambda, DynamoDB, S3}}{}
          \resumeItemListStart
            \resumeSubItem{Finalist in a hackathon with a team of 5. Developed a frontend using React with TypeScript for viewing transcripts, managing comments, and displaying summaries. Implemented a backend with Node.js and AWS Lambda for handling CRUD operations and integrating with an LLM to generate summaries.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, HTML, CSS, Python, SQL} \\
     \textbf{Frontend}{: React.js, Next.js, React Native, TailwindCSS, Material UI } \\
     \textbf{Backend}{: Node.js, Express.js, MongoDB, PostgreSQL, Firebase} \\
     \textbf{Version Control}{: Git, GitHub} \\
     \textbf{Tools}{: Figma, Docker } \\
     \textbf{Concepts}{: Object Oriented Programming, UI/UX Design Principles } \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
