\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muturi David} \\ \vspace{1pt} 
    \textbf{ Software Engineer } \\ \vspace{1pt}
    \href{mailto:muturidavid854@gmail.com}{\textcolor{blue}{muturidavid854@gmail.com}} $|$
    \href{https://linkedin.com/in/tushdev}{\textcolor{blue}{linkedin.com/in/tushdev}} $|$
    \href{https://github.com/tushcmd}{\textcolor{blue}{github.com/tushcmd}} $|$
    \href{https://tushdev.co/}{\textcolor{blue}{tushdev.co}}
\end{center}





%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kenyatta University}{Nairobi, Kenya}
      {B Sc}{Aug. 2021 -- Dec. 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SWE Fellow}{Jul. 2024 -- Present}
      {Headstarter AI}{Track C (Virtual)}
      \resumeItemListStart
        \resumeSubItem{Developing and deploying multiple solo and team projects, including a personal website, pantry tracker, AI customer support system, and AI-powered flashcards and Stripe integration.}
        \resumeSubItem{Worked with technologies including HTML, CSS, ReactJS, NextJS, Firebase, OpenAI API, and AWS.}
        \resumeSubItem{Collaborated in teams to build scalable and efficient web applications, culminating in a final project and presentation.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full Stack Developer}{Jan. 2024 -- Jun. 2024}
      {Freelance}{Remote}
      \resumeItemListStart
        \resumeSubItem{Designed and implemented dynamic websites and web applications using React, Next.js, Node.js, and MongoDB.}
        \resumeSubItem{Built RESTful APIs and integrated with third-party services to enhance functionality.}
        \resumeSubItem{Collaborated with clients to deliver custom solutions tailored to their business needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
          {\textcolor{blue}{\href{https://flash-cards-five-xi.vercel.app/}{AI Flashcards SaaS}}}{Aug. 2024}{\emph{Next.js, Clerk, Firebase, OpenAI, Stripe}}{}
          \resumeItemListStart
            \resumeSubItem{Built a flashcard SaaS application with authentication, payment integration, and OpenAI-powered flashcard generation. \textbf{Demo:} \href{https://flash-cards-five-xi.vercel.app/}{https://flash-cards-five-xi.vercel.app/}.}
            \resumeSubItem{Implemented CRUD features with Firebase Firestore and handled subscriptions using Stripe.}
          \resumeItemListEnd
          
      \resumeSubheading
          {\textcolor{blue}{\href{https://razzo-zeta.vercel.app/}{raZZo}}}{Apr. 2024}{\emph{Next.js, Radix, Framer Motion, React Hook Form, Zod}}{}
          \resumeItemListStart
            \resumeSubItem{Designed a sleek, multi-page car hire landing page using Next.js, integrated with advanced UI components from Radix and React Three Fiber for a futuristic look. The project features responsive design, animations with Framer Motion, and form handling with React Hook Form and Zod.}
          \resumeItemListEnd
          
      \resumeSubheading
          {\textcolor{blue}{\href{https://next-dev-starter.vercel.app/}{NextDevStarter}}}{Mar. 2024}{\emph{Next.js, Shadcn, TypeScript, Zod}}{}
          \resumeItemListStart
            \resumeSubItem{A streamlined Next.js project, bootstrapped with create-next-app, featuring TypeScript, dark mode, responsive design, and essential utilities pre-configured for fast, efficient development.}
          \resumeItemListEnd
          
      \resumeSubheading
          {\textcolor{blue}{\href{https://car-inventory-livid.vercel.app/}{Car Inventory}}}{Apr. 2024}{\emph{Next.js, Node.js, MongoDB, Shadcn UI, Tanstack Table, SWR}}{}
          \resumeItemListStart
            \resumeSubItem{Developed a full-stack CRUD application with Next.js for the frontend and Node.js with MongoDB for the backend. Utilized Shadcn UI, Tanstack Table, SWR, and React Hook Form for a responsive and dynamic UI, with features like search implementation, table pagination, and multiple pages.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, HTML, CSS, Python, SQL} \\
     \textbf{Frameworks}{: React.js, Next.js, Node.js, Express.js, TailwindCSS} \\
     \textbf{Tools}{: Git, GitHub, Figma, Vercel, Firebase, Docker} \\
     \textbf{Concepts}{: Object Orinted Programming, UI/UX Design Principles } \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
