\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xcolor}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set link color
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Muturi David} \\ \vspace{1pt} 
    \href{mailto:muturidavid854@gmail.com}
    {\underline{muturidavid854@gmail.com}} $|$
    \href{https://linkedin.com/in/tushdev}{\underline{linkedin.com/in/tushdev}} $|$
    \href{https://github.com/tushcmd}{\underline{github.com/tushcmd}} $|$
    \href{https://tushdev.co/}{\underline{tushdev.co}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kenyatta University}{Nairobi, Kenya}
      {Bachelor of Science, Nursing}{Aug. 2021 -- Dec. 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SWE Fellow}{Jul. 2024 -- Present}
      {SWE Fellowship}{Track C (Virtual)}
      \resumeItemListStart
        \resumeSubItem{Developed and deployed multiple solo and team projects, including a personal website, pantry tracker, AI customer support system, and AI-powered flashcards and Stripe integration.}
        \resumeSubItem{Worked with technologies including HTML, CSS, ReactJS, NextJS, Firebase, OpenAI API, and AWS.}
        \resumeSubItem{Collaborated in teams to build scalable and efficient web applications, culminating in a final project and presentation.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full Stack Developer}{Jan. 2024 -- Jun. 2024}
      {Freelance}{Remote}
      \resumeItemListStart
        \resumeSubItem{Designed and implemented dynamic websites and web applications using React, Next.js, Node.js, and MongoDB.}
        \resumeSubItem{Built RESTful APIs and integrated with third-party services to enhance functionality.}
        \resumeSubItem{Collaborated with clients to deliver custom solutions tailored to their business needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheading
          {Next Dev Starter}{Jun. 2024}{\emph{Next.js, Shadcn, TypeScript, Zod}}{}
          \resumeItemListStart
            \resumeSubItem{Developed a complete starter template for Next.js developers, featuring components with shadcn forms and themes.}
          \resumeItemListEnd
      \resumeSubheading
          {Portfolio Website}{Apr. 2024}{\emph{HTML, CSS, JavaScript, React.js, TailwindCSS}}{}
          \resumeItemListStart
            \resumeSubItem{Built a personal portfolio website showcasing projects and skills, with a modern and responsive design.}
          \resumeItemListEnd
      \resumeSubheading
          {Puns AI}{Jul. 2024}{\emph{Next.js, OpenAI API, Vercel}}{}
          \resumeItemListStart
            \resumeSubItem{Created an application that generates puns based on user input using OpenAI's API.}
          \resumeItemListEnd
      \resumeSubheading
          {Gitlytics}{Jun. 2023 -- Present}{\emph{Python, Flask, React, PostgreSQL, Docker}}{}
          \resumeItemListStart
            \resumeSubItem{Developed a full-stack web application with Flask serving a REST API and React as the frontend.}
            \resumeSubItem{Implemented GitHub OAuth to fetch data from user repositories and visualize GitHub collaboration data.}
            \resumeSubItem{Utilized Celery and Redis for asynchronous task management.}
          \resumeItemListEnd
      \resumeSubheading
          {Simple Paintball}{May 2022 -- May 2024}{\emph{Spigot API, Java, Maven, TravisCI, Git}}{}
          \resumeItemListStart
            \resumeSubItem{Developed a Minecraft server plugin for entertainment, achieving 2K+ downloads and an average 4.5/5-star review.}
            \resumeSubItem{Implemented continuous delivery using TravisCI to build the plugin upon new releases.}
            \resumeSubItem{Collaborated with Minecraft server administrators to gather feedback and suggest new features.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, HTML, CSS, Python, SQL} \\
     \textbf{Frameworks}{: React.js, Next.js, Node.js, Express.js, TailwindCSS, Docker} \\
     \textbf{Tools}{: Git, GitHub, Figma, Vercel, AWS, Firebase} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
